Figures

### 2023-02-21 figures/figures.Rmd
data loading

```{r}
source("../scripts/99_utils.R")
```

>>>>

```{r}
if(dir.exists("../scripts")){
    source("../scripts/99_utils.R")
}else{
    source("scripts/99_utils.R")
}

dt <- read.csv(
    "../../Data/Euroflux/BE-Lon/L2-L4_2004-2012/EFDC_L2_Flx_BELon_2008_v017_30m.txt",
    header = TRUE,
    colClasses = c("TIMESTAMP_START" = "character", "TIMESTAMP_END" = "character"), 
    na.strings = "-9999") %>%
    clean_names()

head(dt)
```
